{Contextual Learning with Integrated Least Effort Knowledge Networks}

### 2016-10-25 proposal.tex
tiny rewording in proposal

To contextualize knowledge in an abstract manner, we develop the SKN
framework ({\bf S}cale-free {\bf K}nowledge {\bf N}etwork). Knowledge is
represented as distinct atoms of information and their relations in the
structure of a connected network. The network is constructed by preferential
``least effort'' attachment \cite{barabasi99}\cite{cancho03}, where the
learning of a new atom of knowledge joins the network with relations to the
contextual knowledge from which it was learned. This network is scale-free
--- it conforms to a mathematical pattern similar to that of Zipf's Law
\cite{zipf49}, where the degree of connectivity for nodes in the network
follow a class of power law distributions.

>>>>

To contextualize knowledge in an abstract manner, we develop the SKN
framework ({\bf S}cale-free {\bf K}nowledge {\bf N}etwork). Knowledge is
represented as distinct atoms of information and their relations in the
structure of a connected network. The network is constructed by preferential
``least effort'' attachment \cite{barabasi99}\cite{cancho03}, where a new
atom of knowledge joins the network with relations to the contextual
knowledge from which it was learned. This network is scale-free --- it
conforms to a mathematical pattern similar to that of Zipf's Law
\cite{zipf49}, where the degree of connectivity for nodes in the network
follow a class of power law distributions.
